GVN-hoist: hoisting expressions from control flow

### 2016-08-04 hoist.tex
clean a bit the related work

@@

\section{Global Value Numbering}
\section{Code Hoisting}
Code hoisting does not remove redundancies by itself but it enables
removal of redundancies by other passes.  e.g., Enable inlining.
\section{Related Work}

1. Code hoisting in adjacent blocks in a diamond/triangle like structure.
2. O(n) Algorithm.
3. Hoisting equivalent computations in non-sibling BBs.
4. Hoisting across switch blocks.
5. Hoisting to improve PRE.
6. Hoisting to reduce critical path in OoO execution.
7. Ranking/Wavefront algorithm to hoist across switch blocks.

>>>>

Why hoisting expressions:
\begin{itemize}
\item OOO processors: good for speculative execution of branches
\item more ILP for in-order processors
\item code size
\item optimize for register pressure
\item improve inlining heuristics
\end{itemize}

\begin{enumerate}
\item Code hoisting in adjacent blocks in a diamond/triangle like structure.
\item O(n) Algorithm.
\item Hoisting equivalent computations in non-sibling BBs.
\item Hoisting across switch blocks.
\item Hoisting to improve PRE.
\item Hoisting to reduce critical path in OoO execution.
\item Ranking/Wavefront algorithm to hoist across switch blocks.
\end{enumerate}

\section{Related Work}

A lot of bug reports in GCC and LLVM bugzillas, no papers on this topic yet.

Code hoisting does not remove redundancies by itself but it enables
removal of redundancies by other passes.  e.g., Enable inlining.

@@

\subsection{Global Value Numbering}
